\thispagestyle{empty}
\noindent
\begin{center}
    {\Large \textbf{Letter of Transmittal}}
\end{center}

\vspace{0.8cm}

\noindent
\today \\[0.3cm]
The Director \\
Institute of Information and Communication Technology (IICT) \\
Shahjalal University of Science and Technology, Sylhet \\

\vspace{0.4cm}

\noindent
\textbf{Subject:} Submission of Internship Report for SWE--420.

\vspace{0.5cm}

\noindent
Dear Sir,

\vspace{0.3cm}

\noindent
With profound respect and great pleasure, I am submitting my internship
report for the course \textbf{SWE--420}, undertaken in my eighth semester
as a partial fulfilment of the Bachelor of Science in Software Engineering
program. I successfully completed a full-time internship at
\textbf{FlowGenX AI} from \textbf{10\textsuperscript{th} November 2025} to
\textbf{02\textsuperscript{nd} May 2026}, working remotely from
Bangladesh in the position of \emph{Full Stack Software Engineer --
Generative AI (Intern)}.

\vspace{0.3cm}

\noindent
This report reflects the technical knowledge, professional skills, and
practical industry exposure I gained during the program. Under the
supervision of \textbf{Mr.~Abrar Bin Rofique}, Software Engineer (Gen AI),
and the guidance of \textbf{Mr.~Sanjib Sen}, Senior Software Engineer and
Team Lead, I had the opportunity to contribute to FlowGenX AI's
\texttt{runtime\_connectivity} project --- the company's unified
connectivity framework that powers integrations with more than two hundred
external services. The report describes the company, the engineering
processes I followed, the projects I contributed to, the skills I
developed, and the personal reflections from my internship journey.

\vspace{0.3cm}

\noindent
I have prepared this report with sincere effort and care so that it
reflects both the depth of my engagement with the company and the academic
standards expected by the department. I would be honoured by your kind
review and acceptance of this report.

\vspace{0.8cm}

\noindent
Yours sincerely, \\[0.6cm]
\textbf{Md. Rakibul Kabir} \\
Registration No.: 2020831051 \\
Session: 2020--2021 \\
Department of Software Engineering \\
Institute of Information and Communication Technology \\
Shahjalal University of Science and Technology, Sylhet

\newpage
