\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

First and foremost, I would like to express my heartfelt gratitude to the
\textbf{Department of Software Engineering} and the \textbf{Institute of
Information and Communication Technology (IICT)} at Shahjalal University
of Science and Technology, and to \textbf{FlowGenX AI}, for jointly
making this six-month internship possible. Without their combined effort
this transformative experience would not have happened.

\vspace{0.2cm}

I am deeply grateful to the academic faculty of IICT, SUST, especially
\textbf{Dr.~Mohammad Reza Selim}, the \emph{Honourable Director} of
the Institute of Information and Communication Technology, and
\textbf{Mr.~Mahfuzur Rahman Emon}, Lecturer, for coordinating the
internship placement programme and giving students like me the
opportunity to gain hands-on industry experience before graduation.

\vspace{0.2cm}

I owe my deepest and most personal thanks to \textbf{Mr.~Sumon Saha},
\textbf{Founder \& CEO of FlowGenX AI}. Sumon Sir did not simply offer
me an internship; he offered me a front-row seat --- the rare privilege
of working directly alongside him and the brilliant senior engineers
he has gathered around him. He opened door after door of opportunity
that an intern in my position could not have hoped for, gave me real
responsibility paired with the flexibility to grow into it, and
personally took the time to teach me advanced developer tools and
modern engineering practices that I had not encountered in my academic
life. Despite the relentless demands on his calendar as a founder, he
never once made me feel that any of my questions were too small or
any of my concerns unworthy of his attention; he heard me out, helped
me through, and never spoke a single unkind word in any of our
interactions. If I missed a meeting for any reason, he would notice
and gently follow up to make sure I was alright. That kind of human
care, extended by someone of his stature to an intern, is something
I will carry with me through the rest of my career.

\vspace{0.2cm}

I am also thankful to \textbf{Mr.~Balaji Sundara}, \emph{Vice
President of GTM and Growth} at FlowGenX AI, for the strategic
guidance that gave context and direction to the larger picture of the
work I was contributing to.

\vspace{0.2cm}

I would like to extend my deepest appreciation to my immediate supervisor,
\textbf{Mr.~Abrar Bin Rofique}, Software Engineer (Gen AI), whose
day-to-day mentorship, code reviews, and patient explanations were
absolutely central to my growth. His willingness to answer every doubt
--- no matter how small --- and his insistence on quality over speed
shaped the way I now think about software engineering. I am equally
thankful to my additional mentor \textbf{Mr.~Ashikuzzaman Abir},
Software Engineer, who supports the workflow-agent side of the platform
and who patiently walked me through how a connector becomes a callable
node inside an end-to-end agent workflow whenever my work crossed that
boundary.

\vspace{0.2cm}

My sincere thanks also go to my \textbf{Team Lead Mr.~Sanjib Sen},
\emph{Senior Software Engineer}, for his architectural guidance,
constructive feedback in pull requests, and trust in assigning me
production-grade work. I am equally indebted to my closest teammates
\textbf{Mr.~Nayem Islam} \emph{Software Engineer} and \textbf{Mr.~Latiful Kabir} \emph{Software Engineer}, both of whom
collaborated with me daily on the connectivity team, shared their
expertise generously, and made remote teamwork feel genuinely warm.

\vspace{0.2cm}

Finally, I would like to thank every member of the FlowGenX AI engineering,
product, and operations teams whose collective effort makes the platform
what it is today. Their cooperation, openness to ideas, and shared
commitment to building a globally relevant product made every working
day feel meaningful. The lessons I leave with are not only technical;
they are about how a small, ambitious team builds a serious product
across continents.

\vspace{0.6cm}

\hfill\textbf{Md.~Rakibul Kabir}

\newpage
