\chapter*{Executive Summary}
\addcontentsline{toc}{chapter}{Executive Summary}

This report documents my internship experience at \textbf{FlowGenX AI},
a Silicon Valley-based software company building an
\emph{Agentic Integration Platform} that lets enterprises design,
orchestrate, and deploy AI agents and workflows from a single,
no-/low-code interface. The internship was undertaken as the partial
fulfilment of the SWE--420 Internship course of the Bachelor of Science
in Software Engineering program offered by the Department of Software
Engineering, Institute of Information and Communication Technology
(IICT), Shahjalal University of Science and Technology, Sylhet.

\vspace{0.2cm}

I joined FlowGenX AI as a \emph{Full Stack Software Engineer --
Generative AI (Intern)} on \textbf{10 November 2025} and worked
full-time, remotely from Bangladesh, through \textbf{02 May 2026} ---
a tenure of approximately five and a half months that exceeded the
four-month minimum stated in my offer letter. From the first week, I
was treated as a contributing member of the connectivity team and
trusted with production-grade work that ships to real users on the
FlowGenX platform.

\vspace{0.2cm}

The bulk of my contribution was to FlowGenX's \texttt{runtime\_connectivity}
project --- a unified Python framework that exposes more than two
hundred third-party services (databases, cloud storage, SaaS APIs, AI
providers, and more) through a single standardised interface. Across
the internship I authored 178 commits and delivered more than 90
production-ready connectors, each implemented end-to-end against the
project's three-tier abstraction (\texttt{BaseManager} →
\texttt{DBManager}/\texttt{FSManager}/\texttt{ObjManager}), validated
through dedicated integration test scripts, and accompanied by
auto-generated OpenAPI metadata that drives the platform's frontend.
Beyond feature work, I owned several reliability improvements (OAuth2
token-refresh, retry logic, encoding fixes), refactoring efforts (the
DataFrame/list duality across SQL connectors, a clean separation of the
Anthropic Files and Skills APIs, the AWS Textract reorganisation), and
documentation deliverables (UI Endpoint Test Reference docs for many
high-value connectors).

\vspace{0.2cm}

The internship also exposed me to the engineering culture of a fast-paced,
globally distributed startup: a disciplined feature-branch Git workflow,
disciplined code review, automated metadata regeneration pipelines,
clean code enforced through Black/isort/Ruff and pre-commit hooks,
\texttt{uv}-managed Python environments, and asynchronous Google Chat /
Google Meet collaboration across the United States and Bangladesh
timezones. Beyond \texttt{runtime\_connectivity}, I gained working
exposure to Apache Airflow (used by FlowGenX's workflow engine),
FastAPI, the Model Context Protocol (MCP), and the Agent-to-Agent (A2A)
communication patterns at the heart of the company's agentic stack.

\vspace{0.2cm}

This report is organised into seven chapters. Chapter~1 introduces the
report and its scope. Chapter~2 profiles FlowGenX AI as an organisation.
Chapter~3 describes the software engineering process I followed at the
company. Chapter~4 narrates the internship activities themselves,
including the onboarding learning phase and the live project work.
Chapter~5 catalogues the technical and non-technical skills I acquired.
Chapter~6 reflects on what daily life as a remote intern at a
distributed startup looked like. Chapter~7 concludes the report with a
personal reflection on the experience and what it means for my future
career.

\newpage
