\chapter*{References}
\addcontentsline{toc}{chapter}{References}

The following sources have been consulted in the preparation of this
report. URLs were last verified at the time of submission.

\begin{enumerate}[leftmargin=*]
    \item FlowGenX AI --- Official Website. \\
    \texttt{https://www.flowgenx.ai/}

    \item FlowGenX AI --- About Page (mission, vision, capabilities). \\
    \texttt{https://www.flowgenx.ai/about}

    \item FlowGenX AI --- Platform Overview. \\
    \texttt{https://www.flowgenx.ai/platform/workflow-development} \\
    \texttt{https://www.flowgenx.ai/platform/work-ai} \\
    \texttt{https://www.flowgenx.ai/platform/integration-studio} \\
    \texttt{https://www.flowgenx.ai/platform/knowledgebase} \\
    \texttt{https://www.flowgenx.ai/platform/security-governance} \\
    \texttt{https://www.flowgenx.ai/platform/agent-fabric}

    \item FlowGenX AI --- Use Cases. \\
    \texttt{https://www.flowgenx.ai/usecases}

    \item FlowGenX AI --- Templates. \\
    \texttt{https://www.flowgenx.ai/templates}

    \item FlowGenX AI --- Frequently Asked Questions. \\
    \texttt{https://www.flowgenx.ai/FAQ}

    \item FlowGenX AI --- Developer Documentation. \\
    \texttt{https://docs.flowgenx.ai/}

    \item FlowGenX AI --- Engineering Blog. \\
    \texttt{https://blog.flowgenx.ai/}

    \item FlowGenX AI --- LinkedIn Page. \\
    \texttt{https://www.linkedin.com/company/flowgenx-ai/}

    \item FlowGenX AI --- Application Platform. \\
    \texttt{https://platform.flowgenx.ai/}

    \item Internal documentation of the
    \texttt{runtime\_connectivity}, \texttt{runtime\_apis}, and
    \texttt{runtime\_components} repositories of FlowGenX AI
    (referenced with the company's permission; specific contents
    omitted under confidentiality).

    \item Author's personal Git commit history on the
    \texttt{runtime\_connectivity} repository, period 12 November 2025
    -- 02 May 2026.

    \item Author's internship offer letter, dated 22 October 2025,
    issued by FlowGenX AI.

    \item Anthropic --- Claude Developer Documentation. \\
    \texttt{https://docs.anthropic.com/}

    \item OpenAI --- API Reference. \\
    \texttt{https://platform.openai.com/docs/}

    \item Amazon Web Services --- Amazon Rekognition Developer Guide. \\
    \texttt{https://docs.aws.amazon.com/rekognition/}

    \item Amazon Web Services --- Amazon Textract Developer Guide. \\
    \texttt{https://docs.aws.amazon.com/textract/}

    \item Apify --- API Documentation. \\
    \texttt{https://docs.apify.com/api/v2}

    \item Apache Airflow --- Documentation. \\
    \texttt{https://airflow.apache.org/docs/}

    \item FastAPI --- Documentation. \\
    \texttt{https://fastapi.tiangolo.com/}

    \item Pydantic --- Documentation. \\
    \texttt{https://docs.pydantic.dev/}

    \item Model Context Protocol --- Specification. \\
    \texttt{https://modelcontextprotocol.io/}

    \item Department of Software Engineering, Institute of Information
    and Communication Technology, Shahjalal University of Science and
    Technology --- SWE--420 Course Syllabus.
\end{enumerate}
