\chapter{Skills Acquired}
\label{ch:skills}

This chapter catalogues the skills I acquired during my internship at
FlowGenX AI. They fall into two broad categories: technical skills,
which I developed through the day-to-day work on the
\texttt{runtime\_connectivity} project and the surrounding repositories,
and non-technical skills, which I developed through working inside a
remote-first, globally distributed engineering team.

\section{Technical Skills}

\subsection{Programming Languages}
\paragraph{Python (Python 3.11+).}
The primary language of the internship and the one I now use most
fluently. Across five and a half months and 178 commits I wrote idiomatic,
typed, async-aware Python: Pydantic models, decorators, context managers,
generators, dataclasses, asyncio coroutines, pytest fixtures, and
mocking patterns. Black, isort, Ruff, and pre-commit hooks made the
``correct shape'' of clean Python second nature.

\paragraph{SQL.}
Daily exposure across PostgreSQL (the platform's metadata store as well
as a connector), MySQL, Microsoft SQL Server, and several cloud
managed-database variants (AWS RDS, Azure SQL). I wrote the standard
range of CRUD, schema inspection, and bulk-write logic, plus the
parameter standardisation work that unified how SQL connectors accept
both DataFrames and raw lists of records.

\paragraph{TypeScript and JavaScript.}
Read-level fluency across the Next.js frontend and the Node.js-based
tooling. While my own contributions were primarily backend, I
regularly read frontend code to understand how the UI consumed the
auth-config and OpenAPI metadata my connectors produced.

\paragraph{Configuration languages.}
JSON (heavy use, including hand-edited OpenAPI specs and
configuration), YAML (CI configuration, Docker Compose, Kubernetes
manifests), and TOML (\texttt{pyproject.toml} for the Python
projects).

\subsection{Frameworks and Libraries}
\paragraph{FastAPI and Pydantic.}
The pair sit at the centre of the platform's backend. I worked with
FastAPI patterns through the runtime APIs and used Pydantic
extensively to model connection parameters, request schemas, and
response shapes for every connector.

\paragraph{Apache Airflow.}
The workflow engine underneath \texttt{runtime\_apis}. I learned how
DAGs are defined, scheduled, and triggered, and how the connectors I
shipped become callable nodes inside those DAGs.

\paragraph{Pandas.}
Used for in-memory DataFrame transformations in the database and file
connectors --- and for the DataFrame/list duality I introduced into
the SQL write methods.

\paragraph{boto3 and the AWS SDK.}
Used pervasively in the AWS connectors --- S3, RDS, Textract,
Rekognition. I worked with boto3 paginators, signed-request flows,
multipart uploads, asynchronous job patterns, and IAM credential
handling.

\paragraph{Other libraries.}
\texttt{requests} and \texttt{httpx} for HTTP, \texttt{asyncio} for
asynchronous code paths, \texttt{pytest} (with fixtures, mocks, and
integration markers) for testing, and \texttt{Jinja2} as used by the
runtime components for runtime-parameterised configuration.

\subsection{Databases}
Hands-on familiarity with a wide range of database backends through
the connectors I built and tested:

\begin{itemize}[leftmargin=*]
    \item \textbf{Relational:} PostgreSQL, MySQL, Microsoft SQL
    Server, Azure SQL Server, AWS RDS PostgreSQL, AWS RDS MySQL,
    Snowflake.
    \item \textbf{Document and NoSQL:} MongoDB.
    \item \textbf{Search:} Elasticsearch, Typesense.
    \item \textbf{Vector databases:} Pinecone, Weaviate, Milvus.
\end{itemize}

For each I learned the connection model, the authentication options,
the standard CRUD shape, the pagination model, and the
performance-relevant operations (bulk insert, upsert, truncate).

\subsection{Cloud Platforms}
\paragraph{Amazon Web Services.}
Direct work with S3 (bucket policies, versioning, multipart uploads),
RDS for both PostgreSQL and MySQL, Textract (sync and async document
analysis with adapters), Rekognition (image, video, face, custom
labels, stream processors), and IAM credential flows.

\paragraph{Microsoft Azure.}
Direct work with Blob Storage, Data Lake, and Azure SQL Server (with
firewall-rule mode selection and retry logic).

\paragraph{Google Cloud and Microsoft 365.}
Connector-level work on Google Tasks, Google Forms, Google Chat,
Google Meet, and Microsoft 365 (OneDrive and SharePoint).

\subsection{AI / LLM Providers and Generative-AI Patterns}
\paragraph{Provider connectors.}
Built and tested connectors for OpenAI (assistants, models, threads),
Anthropic (messages, batch, files, models, the Skills API), Google
Gemini, xAI, Groq, DeepSeek, and Perplexity AI.

\paragraph{Vector search and embeddings.}
Built connectors for Pinecone, Weaviate, and Milvus, which gave me
working familiarity with vector embeddings, similarity search,
metadata filtering, and the role these systems play inside
Retrieval-Augmented Generation (RAG) pipelines.

\paragraph{Agentic patterns.}
Working inside FlowGenX exposed me to the practical use of multi-agent
patterns --- ReAct, Supervisor, Swarm, and Deep agent patterns ---
and to the protocols underneath them: the \emph{Model Context
Protocol (MCP)} for exposing tools to agents, and \emph{Agent-to-Agent
(A2A)} communication for inter-agent collaboration.

\subsection{Authentication Patterns}
The connector work exposed me to every modern authentication pattern
in production use:

\begin{itemize}[leftmargin=*]
    \item \textbf{OAuth 2.0} with refresh-token flows (the most
    important being the QuickBooks access-token refresh mechanism I
    implemented).
    \item \textbf{API Key} and \textbf{Bearer Token} authentication.
    \item \textbf{HTTP Basic Authentication}.
    \item \textbf{AWS IAM} credentials and signed-request flows.
\end{itemize}

\subsection{System Architecture and Concepts}
\paragraph{Microservices architecture.}
FlowGenX is composed of multiple cooperating services
(\texttt{flowgenx-nextjs-V2}, \texttt{runtime\_apis},
\texttt{runtime\_components}, \texttt{runtime\_connectivity}). Working
inside this gave me a concrete intuition for service boundaries,
package-level interfaces, and the discipline required to evolve a
shared library without breaking its consumers.

\paragraph{REST and OpenAPI 3.0.}
Every connector method I wrote produced OpenAPI metadata via the
\texttt{@openapi\_endpoint} decorator. By the end of the internship
I could read and write OpenAPI 3.0 schemas fluently.

\paragraph{Webhooks and event-driven patterns.}
Implemented webhook configuration for connectors such as Apify and
participated in the broader event-driven model of the FlowGenX
runtime.

\paragraph{gRPC.}
Read-level exposure through the runtime APIs codebase.

\paragraph{Containerisation and orchestration.}
Worked with Docker for local development environments, observed the
Kubernetes and Helm setup the platform uses for production
orchestration, and read enough of the Terraform configuration to
understand how infrastructure is provisioned.

\paragraph{Caching and performance.}
Direct exposure to caching patterns through the connector cleanup
work and the SQL Server retry logic.

\subsection{Testing}
\paragraph{Unit and integration testing with pytest.}
Wrote hundreds of pytest cases across the connectors I delivered,
spanning fixtures, mocks, parameterised tests, and integration
markers.

\paragraph{Live-API integration testing.}
Wrote a dedicated integration test script for every connector,
producing a \textsc{PASS}/\textsc{FAIL}/\textsc{SKIP} report against
real third-party APIs.

\paragraph{End-to-end UI and workflow validation.}
Validated every connector through the platform's API tester, MCP
Playground, and end-to-end workflow execution.

\subsection{Tooling and IDEs}
\begin{itemize}[leftmargin=*]
    \item \textbf{Git and GitHub} --- feature-branch workflow, pull
    requests, code review, merge conflict resolution.
    \item \textbf{ClickUp} --- task tracking, status reporting, and
    sprint visibility.
    \item \textbf{uv} --- the modern, fast Python package manager that
    FlowGenX standardises on.
    \item \textbf{Black, isort, Ruff, pre-commit} --- the code-quality
    toolchain that enforces uniform style across the codebase.
    \item \textbf{Docker and Docker Desktop} --- local container
    development.
    \item \textbf{Visual Studio Code} --- my primary IDE for the
    internship, with Python, Pylance, and Docker extensions.
    \item \textbf{Postman} --- exploration of third-party APIs before
    coding the connector.
    \item \textbf{Google Chat and Google Meet} --- the daily
    communication tools.
\end{itemize}

\section{Non-Technical and Professional Skills}

\subsection{Communication}
Working as the only intern on a remote, distributed team taught me to
write more carefully. I learned to write status updates that were
self-contained (so the reader did not need additional context),
to phrase technical questions in a way that respected the asynchronous
nature of the team, and to surface blockers early in writing rather
than waiting for a synchronous meeting. I also learned to ask
questions in public channels rather than direct messages, so that the
answers benefited the rest of the team and were searchable later.

\subsection{Code Review Etiquette}
Every pull request I opened received review comments, and I came to
appreciate review as one of the highest-value activities a team can
do. I learned to treat every comment as a conversation rather than a
verdict, to push back politely with reasoning when I disagreed, to
ask for clarification when a comment was ambiguous, and to thank
reviewers for catching subtle issues. By the second half of the
internship I was occasionally reviewing teammates' pull requests
myself --- a small but meaningful sign of having earned the team's
trust.

\subsection{Time Management and Self-Direction}
A remote internship with flexible hours requires more self-discipline,
not less. I built the habit of setting a daily intention at the start
of every working day --- usually ``ship one connector to a reviewable
state, fix one bug, or close one documentation deliverable'' --- and
kept honest with myself about what counted as ``done''. The ClickUp
board made this discipline tangible, and the daily flow of pull
requests provided unambiguous evidence of momentum.

\subsection{Cross-Time-Zone Collaboration}
Working from Bangladesh on a team distributed across the United
States required deliberate handoffs. I learned to leave detailed
end-of-day updates so that the United States team could pick up
where I left off, to compose questions that did not require an
immediate reply, and to schedule the small number of synchronous
meetings during the evening overlap window. By the end of the
internship, this kind of asynchronous handoff felt natural.

\subsection{Professionalism and Ownership}
The defining cultural expectation at FlowGenX --- as captured in my
offer letter --- was that interns demonstrate the same commitment,
dedication, and work ethics as full-time team members. I tried to
honour that throughout: every commit message followed the convention,
every pull request was self-reviewed before being opened, every
connector was tested before being declared complete, and every
deliverable was documented for the next person who would touch it.

\subsection{Curiosity and Continuous Learning}
The breadth of technologies on display in just five and a half
months --- 90+ third-party APIs, multiple cloud providers, several
agentic patterns, vector databases, MCP, A2A, Apache Airflow ---
forced a kind of structured curiosity. I learned to read API
documentation efficiently, to skim a codebase for patterns rather
than reading every line, and to keep a running list of ``things I
should circle back to'' that I worked through whenever a connector
shipped.

\subsection{Problem-Solving and Resilience}
Every connector exposed at least one quirky issue: a malformed base
URL, an undocumented rate limit, an authentication flow that worked
on Linux but not Windows. I learned to treat every such issue as a
puzzle with a finite solution rather than a blocker, to consult
upstream documentation and the third-party's developer community
when needed, and to document the resolution clearly enough that the
next person hitting the same issue would not have to start from
scratch.

\subsection{Patience and Attention to Detail}
The OpenAPI sample-backfill work was the clearest example: replacing
placeholder values with real ones across hundreds of endpoints is
the kind of task that has zero glamour and disproportionate impact.
Doing it well taught me that small details (a real example value, a
correct field name, a properly handled pagination token) can be the
difference between a feature that frustrates users and one that
delights them.
